Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-03-04 paper/paper.tex
adding R (boxplots)
pass
pass on intro adn figure 1

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the\MyComment{ network}
traffic against a pre-defined set of rules, which become obsolete
as attackers learn new strategies to circumvent existing defenses.

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{\nids, synthesis, search}

@@

\begin{wrapfigure}[9in]{r}{0.22\textwidth}
    \vspace{-2ex}  
    \centering
    \scalebox{0.9}{  
      \begin{tikzpicture}
        \begin{axis}[
            width = 0.3\textwidth,
            height = 0.2\textwidth,            
            bar width=4pt,
            scaled ticks=false,
            ymajorticks=false,
            ybar stacked,
            enlargelimits=0.05,
            clip=true,
            legend style={at={(0.5,-0.15)},anchor=north,legend columns=-1},          
            xtick=data,
            xticklabel style={rotate=45, font=\tiny},
            tick pos=left,
            nodes near coords,
            every node near coord/.append style={font=\tiny},
            nodes near coords align={vertical},
            symbolic x coords={Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec},]
            \addplot coordinates {(Jan, 114) (Feb, 155) (Mar, 117) (Apr, 159) (May, 110) (Jun, 231) (Jul, 122) (Aug, 167) (Sep, 107) (Oct, 225) (Nov, 148) (Dec, 127)};
        \end{axis}
      \end{tikzpicture}
    }
    \vspace{-3ex}
    \caption{\label{fig:distribution-rules-per-month}2019 new rules.}
\end{wrapfigure}% <---- don't forget this %

@@

This section evaluates sensitivity of \tname{} to the number of
attacks provided on input. Recall that \tname\ uses one example attack
to generate the seed rule (at the Reverse Engineering step) and the
remaining attacks to evaluate soundness of the rule (at the Rules
Creations step). It is expected that the number and variety of
attacks---of the same kind---plays an important role in the
performance of the technique. To answer this research question, we
selected the cases with the highest number of examples of attacks (see
coolumn ``\#~Vars'' on Table~\ref{table:results}), varied the number of
examples, and measured the position of the golden rule at the
rank. For each number of variants $N$, we sampled five sets of size
$N$ to provide as input to the technique.
x

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \Fix{revise}
Network Intrusion Detection Systems (\nids{}) are a popular mechanism
used by system administrators to defend against network attacks. These
systems monitor the network traffic and flag suspicious network
behavior. Signature-based \nids\ do that by checking the\MyComment{ network}
traffic against a pre-defined set of rules, which become obsolete
as attackers learn new strategies to circumvent existing defenses.

@@

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
% \keywords{\nids, synthesis, search}

%% remove on camera-ready
\settopmatter{printacmref=false}

@@

\begin{wrapfigure}[8in]{r}{0.24\textwidth}
    \vspace{-5ex}  
    \centering
    \scalebox{0.9}{  
      \begin{tikzpicture}
        \begin{axis}[
%            label style={font=\scriptsize},
%            tick label style={font=\scriptsize}
            width = 0.3\textwidth,
            height = 0.2\textwidth,            
            bar width=4pt,
            scaled ticks=false,
            ymajorticks=false,
            ybar stacked,
            enlargelimits=0.09,
            clip=true,
            legend style={at={(0.5,-0.15)},anchor=north,legend columns=-1},          
            xtick=data,
            xticklabel style={rotate=45, font=\footnotesize},
            tick pos=left,
            nodes near coords,
            every node near coord/.append style={font=\footnotesize},
            nodes near coords align={vertical},
            symbolic x coords={Jan, Feb, Mar, Apr, May, Jun, Jul, Aug, Sep, Oct, Nov, Dec},]
            \addplot coordinates {(Jan, 114) (Feb, 155) (Mar, 117) (Apr, 159) (May, 110) (Jun, 231) (Jul, 122) (Aug, 167) (Sep, 107) (Oct, 225) (Nov, 148) (Dec, 127)};
        \end{axis}
      \end{tikzpicture}
    }
    \vspace{-4ex}
    \caption{\label{fig:distribution-rules-per-month}2019 new rules.}
\end{wrapfigure}% <---- don't forget this %

@@

This section evaluates sensitivity of \tname{} to the number of
attacks provided on input. Recall that \tname\ uses one example attack
to generate the seed rule (at the Reverse Engineering step) and the
remaining attacks to evaluate soundness of the rule (at the Rules
Creations step). It is expected that the number and variety of
attacks---of the same kind---plays an important role in the
performance of the technique. To answer this research question, we
selected the cases with the highest number of examples of attacks (see
coolumn ``\#~Vars'' on Table~\ref{table:results}), varied the number of
examples, and measured the position of the golden rule at the
rank. For each number of variants $N$, we sampled five sets of size
$N$ to provide as input to the technique.

Table~\ref{fig:impact-number-attacks} shows
results. \Fix{...elaborate...}

\begin{figure}[t!]
\centering
\includegraphics[scale=0.4]{R/scripttag/scripttag.pdf}
\caption{Impact of number of positive examples.}
\label{fig:impact-number-attacks}
\end{figure}
